Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-11 prop.tex
prop.tex \section{Introduction} Add the main result and prospective...

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and computations
are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Piccinini2015}.
Yet, for centuries, the mathematical formalization of such processes
has been founded on the infinitely precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
Our purpose here is to exploit the consequences of replacing infinitely-specified
quantum probabilities by finite number of intervals used in interval-valued
probability measures; in particular, we show that a quantum interval-valued
probability measure may not be induced by a infinitely-precise state,
but it might be more and more likely to be identified to a particular
state when the measurement resources increase.

@@

We will begin by reviewing existing work that recasts classical probability
spaces in a resource-aware setting and move to aim at recasting quantum
probability and hence quantum measurement to a corresponding resource-aware
setting. In particular, we develop a measurement framework based on
quantum interval-valued probabilities measures. 
\begin{itemize}
\item Assess the validity of fundamental theorems of quantum mechanics,
such as Gleason~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum},
Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
in a quantum formulation stripped away of infinite resources. We will
aim to provide a definite answer to the Meyer-Mermin debate~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}
on the impact of finite precision measurements on the relevance of
the Kochen-Specker theorem. 
\end{itemize}

>>>>

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and computations
are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Piccinini2015}.
Yet, for centuries, the mathematical formalization of such processes
has been founded on the infinitely precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
Our purpose here is to exploit the consequences of replacing infinitely-specified
quantum probabilities by finite number of intervals used in interval-valued
probability measures~(IVPM); in particular, we show that a quantum
interval-valued probability measure may not be induced by a infinitely-precise
state, but it might be more and more likely to be identified to a
particular state when the measurement resources increase.

@@

We will begin by reviewing existing work that recasts classical probability
spaces in a resource-aware setting and move to aim at recasting quantum
probability and hence quantum measurement to a corresponding resource-aware
setting. In particular, we develop a measurement framework based on
quantum interval-valued probability measures. Surprisingly, we found
a quantum IVPM which can not be induced by a state while Shapley proved
a classical convex IVPM can always be induced by a classical ``state''~\cite{Shapley1971,Grabisch2016},
and Gleason proved a infinitely-specified quantum probabilities measure
can always be induced by a quantum state~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Nevertheless, a quantum IVPM could still correspond to many states
while we break it into pieces. Our examples also suggest that a quantum
IVPM could be more and more likely induced by a state while the intervals
become sharper, i.e., the measurement resources increase.

Since Gleason's theorem supports the idea of von Neumann to formulate
quantum states as points in a projective Hilbert space, a point in
a projective Hilbert space might not be the adequate imprecise quantum
``state.'' Instead, a quantum state might be more like an interactive
system suggested by Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which would be different for different interactor. Furthermore, the
fundamental theorems of quantum mechanics followed up by Gleason's
theorem , such as Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
might need to be reassessed the validity with imprecise measurement.
Our research then might provide a new insight to the old debate whether
finite precision measurement would nullify the Kochen-Specker theorem
or not, by Meyer, Mermin, and others~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.
